### 2013-11-22 research/paper/results/results-2.3.tex
Committing small changes to th mathematical model and some initial changes to the results section
Committing some changes to results, still working

\subsection{Displacement,velocity and power output as a function of reduced velocity}

 The quasi-steady analysis data reveals that the displacement amplitude tend to grow with increasing $U^*$ (Fig.\ref{fig:uncollapsed_data} (a) and (b)). The onset of galloping is delayed with increasing $\zeta$ for both high and low Reynolds numbers. This echo the findings of previous studies by \cite{Parkinson1964} and \cite{Barrero-Gil2010a}. Hysteresis could be observed for the case with a higher Reynolds number. Different solutions could be obtained by manipulating the initial conditions (initial displacement) of the system. The upper branch was obtained by giving an initial displacement which was higher than the expected amplitude while the lower branch was obtained by providing a lower initial displacement than the expected amplitude. Although a third state could be simulate theoretically, it was not possible to achieve numerically. This was also observed by \cite{Vio2007}.

@@

 The mean power grows, peaks and then reduces as $U^*$ is increased (Fig.\ref{fig:uncollapsed_data} (e) and (f)) for each value of $\zeta$. The value of  \ustar at which the peak power occur increases with $\zeta$. However, the magnitude of the peaks remain constant for all the values of $\zeta$.  \cite{Barrero-Gil2010a} also observed a similar behaviour. The higher Reynolds number case clearly showed hysteresis in the power data. The range of hysteresis tend to increase with increasing $\zeta$. It could be observed that unlike VIV the  system has no preferred frequency. Although the onset of galloping and the point where peak power occur at different $U^*$ values when the damping ratio is varied, the peak power remains constant regardless of $U^*$. The efficiency of the system could defined as the ratio of the time average power output to $P_{mean}$ the kinetic energy in the fluid per which is $\rho U^3\frac{D}{2}$(similar to \cite{Barrero-Gil2010a}). It was found out that the  system has a peak efficiency of  $0.26\%$  for \reynoldsnumber=165 and $6.7\%$ for \reynoldsnumber=22300. The peak efficiency in \cite{Barrero-Gil2010a} is approximately $5\%$ than what this study obtained. This difference is due to \cite{Barrero-Gil2010a} using a $3^{rd}$ order polynomial as the interpolating polynomial which under predicts the forcing near where the maximum force occurs as compared to the $7^{th}$ order polynomial used in this study.

>>>>

\subsection{Displacement, velocity and power output as a function of reduced velocity}

 The quasi-steady analysis data reveal that the displacement amplitude grows with increasing $U^*$. This is shown for both the high and low \reynoldsnumber\ cases in figures \ref{fig:uncollapsed_data} (a) and (b). The onset of galloping is delayed with increasing damping ratio $\zeta$ for both high and low Reynolds numbers. This echos the findings of previous studies by \cite{Parkinson1964} and \cite{Barrero-Gil2010a}. Hysteresis could be observed for the case with a higher Reynolds number. Different solutions could be obtained by manipulating the initial conditions (initial displacement) of the system. The upper branch was obtained by giving an initial displacement which was higher than the expected amplitude while the lower branch was obtained by providing a lower initial displacement than the expected amplitude. Although theory shows a possible third state, it is an unstable branch and as such it could not be achieved numerically. This was also observed by \cite{Vio2007}.

@@

 The mean power grows, peaks and then slightly reduces as the reduced velocity $U^*$ is increased. This is shown in figure \ref{fig:uncollapsed_data}(e) and (f) for each value of $\zeta$. The value of  \ustar\ at which the peak power occurs increases with $\zeta$. However, the magnitude of the peaks remain constant for all the values of $\zeta$. \citet{Barrero-Gil2010a} also observed a similar behaviour. The higher Reynolds number case clearly shows hysteresis in the power data. The range of hysteresis increases with increasing $\zeta$.

Unlike VIV, which is a resonant-type phenomenon, the quasi-steady system describing galloping has no strongly preferred frequency. Although the onset of galloping and the value of \ustar\ where peak power occurs varies with the damping ratio $\zeta$, the power extracted remains almost constant for values of \ustar\ beyond that where the peak power occurs.

The efficiency of the system can be defined as the ratio of the time average power output to $P_{mean}=\rho U^3\frac{D}{2}$, the kinetic energy in the fluid approaching the body. A similar definition was given in \citet{Barrero-Gil2010a}). The current results show that the system has a peak efficiency of $0.26\%$  for $\reynoldsnumber=165$ and $6.7\%$ for $\reynoldsnumber=22300$. The peak efficiency reported in \citet{Barrero-Gil2010a} for \JL{KASUN: include the Re from Barrero-Gil} is approximately $5\%$ less than the current result. This difference is due to \cite{Barrero-Gil2010a} using a $3^{rd}$ order polynomial as the interpolating polynomial which under predicts the forcing at values of $\theta$ where the maximum force occurs as compared to the $7^{th}$ order polynomial used in this study.

\JL{Up to here 12.20pm}
